Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-03-26 ms.tex
typo
removing stray todo

There has been considerable effort to recover these planetary signals, and to date six
planets have been confirmed in the \KT\ data
\citep{Vanderburg15, Crossfield15, Armstrong15b}.
What is common to all of these methods are that removal of systematics is considered a
step to be undertaken before the search for planets.
Under this strategy, it is implicitly assumed that the systematics are removed perfectly,
while retaining all of the astrophysical signal.
Of course, it is impossible to perfectly separate the astrophysical and instrumental
signal, and such a technique is prone to either over-fitting, in which some of the
astrophysical signal is also removed, or under-fitting, in which some
of the instrumental systematics remain.
A better strategy is to simultaneously fit both the signal and the systematics, as is common
practice in cosmology and, increasingly, in radial velocity searches for planetary systems
\citep[e.g.][]{Ferreira00, Boisse11, Haywood14, Grunblatt15}.

@@

\begin{figure*}[htbp]
\centerline{\includegraphics[width=1.0\textwidth]{f2}}
\caption{\btmtodo{PLACEHOLDER, UPDATE. Needs transit models}.
Phase-folded \KT\ photometry for all planet candidates analyzed in
this paper.
Each is the product of a fiducial noise model, in which the median systematic
has been removed for illustrative purposes.
The systems which we validate as transiting planets are labeled in
blue.
The systems which we confirm as false positive events are labeled in red.
The systems which we leave as candidates are labeled in black.
Red curves outline the median transit model for each candidate system.
}
\label{fig:transits}
\end{figure*}

@@

The photometric apertures used to detect these candidates range in radius from
$10\farcs0$ to $19\farcs9$.  In order to be a plausible contaminant,
any companion star must
be either within this aperture or just outside but bright
enough for signficant flux to leak in.
Evaluating each of the systems listed in Table 5, we judge that we cannot yet
rule out contamination as a potential source of the transit signal for four
candidates: 201295312.01, 201403446.01, 201546283.01, 201828749.01.  Despite receiving
low FPP scores from \texttt{vespa}, we list these systems as candidates in
Table 4, rather than planets.  Further updates to the \texttt{vespa} code
will allow consideration of ``specific'' false positive scenarios; that is,
scenarios that correspond to actually detected stars such as these, rather than
hypothetical background or bound companions.

@@

\acknowledgements
We thank Eric Agol (UW), Dan Huber (Sydney) and Jeff Coughlin (SETI) for
conversations and suggestions which improved the quality of this manuscript.

>>>>

There has been considerable effort to recover these planetary signals, and to date six
planets have been confirmed orbiting three stars in the \KT\ data
\citep{Vanderburg15, Crossfield15, Armstrong15b}.
What is common to all of these methods are that removal of systematics is considered a
step to be undertaken before the search for planets.
Under this strategy, it is implicitly assumed that the systematics are removed perfectly,
while retaining all of the astrophysical signal.
Of course, it is impossible to perfectly separate the astrophysical and instrumental
signal, and such a technique is prone to either over-fitting, in which some of the
astrophysical signal is also removed, or under-fitting, in which some
of the instrumental systematics remain.
A better strategy is to simultaneously fit both the signal and the systematics, as is common
practice in cosmology and, increasingly, in radial velocity searches for planetary systems
\citep[e.g.][]{Ferreira00, Boisse11, Haywood14, Grunblatt15}.

@@

\begin{figure*}[htbp]
\centerline{\includegraphics[width=1.0\textwidth]{f2}}
\caption{Phase-folded \KT\ photometry for all planet candidates analyzed in
this paper.
Each is the product of a fiducial noise model, in which the median systematic
has been removed for illustrative purposes.
The systems which we validate as transiting planets are labeled in
blue.
The systems which we confirm as false positive events are labeled in red.
The systems which we leave as candidates are labeled in black.
Red curves outline the median transit model for each candidate system.
}
\label{fig:transits}
\end{figure*}

@@

The photometric apertures used to detect these candidates range in radius from
$10\farcs0$ to $19\farcs9$.  In order to be a plausible contaminant,
any companion star must
be either within this aperture or just outside but bright
enough for signficant flux to leak in.
Evaluating each of the systems listed in Table 5, we judge that we cannot yet
rule out contamination as a potential source of the transit signal for four
candidates: 201295312.01, 201403446.01, 201546283.01, and 201828749.01.  
Despite receiving
low FPP scores from \texttt{vespa}, we list these systems as candidates in
Table 4, rather than planets.  Further updates to the \texttt{vespa} code
will allow consideration of ``specific'' false positive scenarios; that is,
scenarios that correspond to actually detected stars such as these, rather than
hypothetical background or bound companions.

@@

\acknowledgements
We thank Roberto Sanchis-Ojeda (Berkeley), Dan Huber (Sydney) and 
Jeff Coughlin (SETI) for
conversations and suggestions which improved the quality of this manuscript.
